Multi-class Overlapping Group Lasso Classification

### 2014-12-19 highdim-paper/paper.tex
Small paper edits plus conclusion

\title{High-Dim Project}

@@

The task of multiclass classification involves the prediction of a class label
$l$ where the number of possible labels is $k>2$. More often than not, the 
original problem is transformed into $k$ binary classification problems, i.e.
$1$--vs.--all classification and positive prediction with the highest 
confidence is selected as the label. This approach has the disadvantage of
having to train $k$ different models.\\

An alternative formulation, direct multiclass classification, tackles this 
problem directly by solving the following $\operatorname{argmax}$ problem:
$$y_i = \operatorname{argmax}_c W_{:c}^T x_i $$
where $W \in \mathcal{R}^{p \times k}$ is a weight matrix, with $W_{ij}$
corresponding to the $i$-th feature of class $j$. In this paper, we refer
to features as elements in the instance data $x$. A feature in $x$ is
associated with $k$ weights in $W$, one for each class.\\

@@

Efficient computation of this objective is possible by storing current 
loss for each data point. Let $A$ be an $n\times k$ matrix where the 
$i,r$-th element corresponds to 
 $(1-(W_{:y_i}^Tx_i - W_{:r}x_i).$
 The gradient can then be calculated as 
 $l^\prime(W)_{j} = \frac{2}{n}\sum_{i=1}^n\sum_{r\ne y_i}
 \max(A_{ir}, 0)(x_{ij}e_{y_i} - x_{ij} e_r)$
where $e_r$ is a $k$ dimensional vector with zeroes everywhere except for a 1
at the $r$-th position. We only have to examine elements in $A$ for which 
the corresponding $x_{ij}$ is non-zero. When $x_{i}$ is sparse, more often
than not $x_{ij}$ is zero and can be ignored.

@@

$$ \min_{W \in R^{d x m}} F(W) = $$
$$\frac{1}{n} \sum_{i=1}^{n} \sum_{r \neq y_i } \max(1 - ( W_{:y_i}^T \cdot x_i - W_{:r}^T \cdot x_i) , 0 )^2 $$
$$ + \lambda \sum_{g \in \mathcal{G}} \sum_{r=1}^{d} \| W_{g,r} \|_2$$ \\

The first term is the multiclass squared hinge loss function. We want the dot product of an instance and its feature vector to be as large as possible, and the dot product of this instance and the rest feature vectors to be as small as possible. And as long as their difference is greater then a margin ($1$ in this case), we won't penalize it. In the second term, $W_{g,r}$ means a block of weights in group $g$ and class $m$. The L2-norm regulization is computed and sum up for each block. The $\lambda > 0$ is a parameter controls the trade-off between the hinge loss and the L2-norm regulization.

@@

Given the co-occurence matrix $Z$, algorithm~\ref{alg:groupgen}  is used to generates groups for the features. The algorithm generates non-overlapping groups. To generate overlapping groups, skip step 3.

@@

\section{Conclusion}
% include your own bib file like this:
\bibliographystyle{acl}
\bibliography{ref}

>>>>

\title{Multi-class Overlapping Group Lasso Classification }

@@

The task of multiclass classification involves the prediction of a class label
$l$ where the number of possible labels is $k>2$. More often than not, the 
original problem is transformed into $k$ binary classification problems, i.e.
$1$--vs.--all classification and the positive prediction with the highest 
confidence is selected as the label. This approach has the disadvantage of
having to train $k$ different models.\\

An alternative formulation, direct multiclass classification, tackles this 
problem directly by solving the following $\operatorname{argmax}$ problem:
$$y_i = \operatorname{argmax}_c W_{:c}^T x_i $$
where $W \in \mathcal{R}^{p \times k}$ is a weight matrix, with $W_{ij}$
corresponding to the $i$-th feature of class $j$. In this paper, we refer
to features as elements in the instance data $x$. A feature in $x$ is
associated with $k$ weights in the row $W_{j:}$, one for each class.\\

@@

\cite{blondel2013block} chose 
$\mathcal{L}_j = \max_c l^{\prime\prime}(W)_{jc}$, the max element of the
Hessian of the loss with respect to the $j$-th row. $\alpha$ is identified
via line search.

Efficient computation of this objective is possible by storing the current 
loss for each data point. Let $A$ be an $n\times k$ matrix where the 
$i,r$-th element corresponds to 
 $(1-(W_{:y_i}^Tx_i - W_{:r}x_i).$
 The gradient can then be calculated as 
 $l^\prime(W)_{j} = \frac{2}{n}\sum_{i=1}^n\sum_{r\ne y_i}
 \max(A_{ir}, 0)(x_{ij}e_{y_i} - x_{ij} e_r)$
where $e_r$ is a $k$ dimensional vector with zeroes everywhere except for a 1
at the $r$-th position. We only have to examine elements in $A$ for which 
the corresponding $x_{ij}$ is non-zero. When $x_{i}$ is sparse, more often
than not $x_{ij}$ is zero and can be ignored.

@@

$$ \min_{W \in R^{d x m}} F(W) = $$
$$\frac{1}{n} \sum_{i=1}^{n} \sum_{r \neq y_i } \max(1 - ( W_{:y_i}^T  x_i - W_{:r}^T x_i) , 0 )^2 $$
$$ + \lambda \sum_{g \in \mathcal{G}} \sum_{r=1}^{d} \| W_{g,r} \|_2$$ \\

The first term is the multiclass squared hinge loss function. We want the dot 
product of an instance and its gold class weight vector to be as large as 
possible, while the dot product with the weight vectors for alternate classes
to be as small as possible. And as long as their difference is greater then 
a margin ($1$ in this case), we won't penalize it.
 In the second term, $W_{g,r}$ means a block of weights in group $g$ and 
 class $m$. The L2-norm regulization is computed and summed up for each block.
The $\lambda > 0$ is a parameter controls the trade-off between the hinge loss
 and the L2-norm regulization.

@@

Given the co-occurence matrix $Z$, algorithm~\ref{alg:groupgen}  is used to
 generate groups of the features. The algorithm generates 
 non-overlapping groups. To generate overlapping groups, skip step 3.

@@

\section{Conclusion}
In this paper, we have presented an extension to the multi-class group lasso,
taking advantage of overlapping groups. In addition we experimented with 
an automatic covariate group generation method using the co occurrence matrix.
Our approach shows promising results, but we still need to improve the 
scalability of this algorithm.

% include your own bib file like this:
\bibliographystyle{acl}
\bibliography{ref}
